---
title: "Psychology Journal Impact Factors"
author: "Daniel N. Albohn"
date: "9/10/2017"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.table.format = "html")
library(tidyverse)
IF <- readr::read_csv('../data/journal_IF.csv') %>% 
  arrange(., desc(`Impact Factor`))
```

Special thanks to the Social Perception and Emotion
Lab and its researchers for supplying the base statistics
for this table. Presently, some of the journal website
links are still broke.

[Read more about impact factors and how to interpret them](http://researchguides.uic.edu/if/impact), or
a thorough explanation and
[critique them](https://blogs.scientificamerican.com/information-culture/understanding-the-journal-impact-factor-part-one/).

If a journal you read or submit to frequently is not on this list, consider
[looking it up](https://jcr.incites.thomsonreuters.com/JCRJournalHomeAction.action?year=&edition=&journal=)
and adding it to the list!

To update this list, please alter the
[data file](../data/journal_IF.csv), and then "re-knit" the [Rmarkdown file](journal_IF.Rmd).

```{r echo=FALSE, warning=FALSE, message=FALSE}
knitr::kable(IF) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

________________________________________________________

Last updated on `r Sys.Date()`